%start
%	Summary
%\vspace{10mm}
% Add the summary section
\summary{%
Research Scientist with EU citizenship and 5+ years of experience in high-frequency trading, market-making, and quantitative finance. Developed and deployed trading algorithms that generated tens of millions USD in revenue. Skilled in mathematical optimization, market microstructure analysis, predictive modeling, and algorithmic trading strategy development, with applications in FX, commodities, equities, and other financial assets.
}

%	WORK EXPERIENCE SECTION

\section{Experience}
\begin{entrylist}
\entry
{09/2022 -- Present}
{Research Scientist}
{Tokyo, Japan}
{\emph{Rakuten}
\begin{itemize}
%	Do not remove these -- start.
    \item Worked closely with FX, CFD, crypto traders, and portfolio managers to identify and resolve production issues, ensuring smooth trading operations.
    \item Created and maintained fully automated trading systems that operate without human intervention, ensuring continuous market engagement that generate \$14M PNL.
	\item Designed high-frequency market-making algorithms boosting pricing precision by 16\% across 15+ currency pairs, reducing market risk and enhancing real-time trading decision-making.
    \item Applied graph theory and community detection techniques (Louvain algorithm and Clique Percolation method) to identify synchronized traders achieving over \$300K in monthly PNL.
%	Do not remove these -- end.
  	\item Created an FX trading optimization framework integrating genetic algorithms and particle swarm optimization to reduce slippage by 20\%.
	\item Analyzed market microstructure to understand the impact of order flow and liquidity on price formation, providing insights for strategy refinement.
    \item Performed extensive backtesting and validation of trading strategies using large-scale datasets with millisecond frequency to ensure robustness and reliability.
	\item Built real-time interactive visualizations to monitor market conditions and trading performance, facilitating quick decision-making (matplotlib, plotly, bokeh, JS callbacks).
 	\item Team lead for the Information Security Management System (ISMS), ensuring compliance with international security standards and safeguarding sensitive trading data.
\end{itemize}
}
\end{entrylist}

%	No LLMs / Generative AI beyond this point.

\begin{entrylist}
\entry
{10/2021 -- 09/2022}
{Visiting Researcher}
{Tokyo, Japan}
{\emph{The University of Tokyo}
\begin{itemize}
	\item Evaluated the influence of the COVID-19 pandemic on residential electricity consumption through a nonlinear autoregressive neural network with exogenous inputs (NARX).
 	\item Developed a Python-based statistical analysis course for students, emphasizing applied statistics and modern code packages with a strong focus on visual outputs.
	\item Guided, trained and advised master's and Ph.D. level students on research techniques, methods and procedures.
\end{itemize}
}

\entry
{09/2019 -- 01/2020}
{Research Scientist}
{Tokyo, Japan}
{\emph{Waseda University}
\begin{itemize}
\item Developed an XGBoost-based algorithm to forecast the flexibility of residential loads, enhancing provincial grid energy efficiency by 10\%.
\item Collaborated with academia and industry in the energy sector in Japan and Canada, presenting my work on demand response to foster innovation and practical application.
\end{itemize}
}
\end{entrylist}
\begin{entrylist}
\entry
{01/2018 -- 03/2018}
{Research Scientist}
{Kyoto, Japan}
{\emph{Kyoto University}
\begin{itemize}
\item Conducted an in-depth analysis of the main opportunities and challenges of the low-emission development strategies of Tokyo’s built environment and synthesized the results in a peer-reviewed publication.
\item Served as a scientific correspondent for various organizations, translating complex scientific research into accessible language for the general public.
\end{itemize}
}
\end{entrylist}
\begin{entrylist}
\entry
{04/2015 -- 04/2016}
{Data Scientist}
{Athens, Greece}
{\emph{Starlight}
\begin{itemize}
\item	Analyzed consumer behavior trends and designed descriptive and predictive modeling algorithms reducing the cost of customer acquisition by 20\%.
\item	Set up and performed A/B tests to optimize UI changes increasing conversion rate by 13\%.
\item	Streamlined data collection processes using scripting and automation tools, increasing data collection efficiency by 50\%.
\end{itemize}}
\end{entrylist}
\begin{entrylist}
\entry
{10/2014 -- 03/2015}
{Data Analyst}
{Athens, Greece}
{\emph{Relay}
\begin{itemize}
\item Automated the process of analysis and visualization of business KPIs (e.g., ticket resolution time) using SQL and Python reducing manual reporting by 5 hours per week.
\item Responded to ad hoc data requests from various departments, providing timely and accurate data analysis.
\end{itemize}
}
\end{entrylist}
%	EDUCATION SECTION
\section{Education}
\begin{entrylist}
\entry
{2018 -- 2021}
{Doctor of Philosophy  (Sustainability Science)}
{Tokyo, Japan}
{\emph{The University of Tokyo}
\begin{itemize}
\item Worked on energy efficiency optimizations in smart grid area networks using a Markov decision process.
\item Japanese government [Monbukagakusho: MEXT] scholarship recipient (awarded 120,000 USD equivalent).
\end{itemize}
}
\end{entrylist}
\begin{entrylist}
\entry
{2016 -- 2018}
{Master of Science (Sustainability Science)}
{Tokyo, Japan}
{\emph{The University of Tokyo}}
\end{entrylist}

\begin{entrylist}
\entry
{2010 -- 2015}
{Bachelor of Science (Economics)}
{Thessaly, Greece}
{\emph{University of Thessaly}}
\end{entrylist}
% skills
\section{Skills}
\begin{skillslist}
  \skill{Programming Languages}{Python, R, SQL}
  \skill{Supporting Technologies}{Git, Docker, SPSS, ArcGIS, Adobe Creative Suite}
  \skill{Techniques}{machine learning, numerical \& algorithmic optimisation, computational statistics, model discrimination}
  \skill{Publications}{7 as first author, 5 as contributing author. Areas including environmental science, energy \& behavioral economics, statistics}
\end{skillslist}
%end
